Study Comparison

### 2023-10-04 analysis/aud_analysis.Rmd
changes to plots

# weekly coughs per min by class and condition
coughs_pl <- coughs %>%
  mutate(week = isoweek(date)) %>%
  filter(week != 6) %>%
  mutate(week = ifelse(week < 6, week - min(week) + 1, week - min(week))) %>%
  group_by(class, week) %>%
  summarize(coughs_per_min = sum(n_coughs) / sum(TT),
            aircleaner = first(aircleaner)) %>%
  ungroup() %>%
  mutate(aircleaner = factor(aircleaner, levels = c("Yes", "No")),
         class = factor(class, levels = c("A", "B"))) %>%
  arrange(class, aircleaner) %>%
  ggplot(aes(x = factor(week), y = coughs_per_min, fill = aircleaner, pattern = class)) +
  geom_bar_pattern(stat = "identity", color = "black", pattern_fill = "white", pattern_angle = 45,
                   pattern_density = 0.25, pattern_spacing = 0.05, width = .5) +
  labs(x = "Study week", y = "Number of coughs per min", fill = "Air cleaner", pattern = "Class", title = "a") +
  scale_fill_manual(values = rev(wes_palette("Royal1")[1:2])) +
  scale_x_discrete(breaks = 1:7) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.05)), breaks = seq(0, 10, 2)) +
  scale_pattern_manual(values = c(A = "stripe", B = "none")) +
  theme_custom() +
  theme(legend.position = "top",
        legend.direction = "horizontal",
        legend.key.width = unit(0.5, "cm"),
        legend.key.height = unit(0.3, "cm"),
        plot.title.position = "plot") +
  guides(fill = guide_legend(nrow = 1, override.aes = list(pattern = "none", order = 2)),
         pattern = guide_legend(nrow = 1, override.aes = list(fill = "white"), order = 1))

@@

save_plot(coughs_pl, pdf_file = "../results/cough-data/coughs-frequency-per-week.pdf", eps_file = "../results/cough-data/coughs-frequency-per-week.eps", w = 12, h = 8)
```

@@

theta_pl
save_plot(theta_pl, pdf_file = "../results/cough-data/coughs-virus-association.pdf", eps_file = "../results/cough-data/coughs-virus-association.eps", w = 12, h = 8)
```

>>>>

# weekly coughs per min by class and condition
coughs_pl <- coughs %>%
  group_by(class, aircleaner) %>%
  summarize(coughs_per_min = sum(n_coughs) / sum(TT)) %>%
  ungroup() %>%
  mutate(aircleaner = factor(aircleaner, levels = c("No", "Yes")),
         class = factor(class, levels = c("A", "B"))) %>%
  arrange(class, aircleaner) %>%
  ggplot(aes(x = aircleaner, y = coughs_per_min, fill = aircleaner)) +
  geom_bar_pattern(mapping = aes(pattern = class),
                   stat = "identity", position = position_dodge(width = .66), color = "black", pattern_fill = "white", pattern_angle = 45,
                   pattern_density = 0.25, pattern_spacing = 0.05, width = .5) +
  geom_text(data = coughs %>% group_by(aircleaner) %>% summarize(coughs_per_min = sum(n_coughs) / sum(TT)) %>% ungroup() %>%
              mutate(y = 4.5),
            mapping = aes(y = y, label = paste("Mean =", round(coughs_per_min, 1))),
            size = 8 / cm(1), vjust = -1) +
  labs(x = "Study week", y = "Number of coughs per min", fill = "Air cleaner", pattern = "Class", title = "a") +
  scale_fill_manual(values = wes_palette("Royal1")[1:2]) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.1)), breaks = seq(0, 10, 2)) +
  scale_pattern_manual(values = c(A = "stripe", B = "none")) +
  theme_custom() +
  theme(legend.position = "top",
        legend.direction = "horizontal",
        legend.key.width = unit(0.5, "cm"),
        legend.key.height = unit(0.3, "cm"),
        plot.title.position = "plot") +
  guides(fill = "none",
         pattern = guide_legend(nrow = 1, override.aes = list(fill = "white"), order = 1))

@@

save_plot(coughs_pl, 
          pdf_file = "../results/cough-data/coughs-frequency-by-condition.pdf", 
          eps_file = "../results/cough-data/coughs-frequency-by-condition.eps", 
          w = 6, h = 8)
```

@@

theta_pl
save_plot(theta_pl, 
          pdf_file = "../results/cough-data/coughs-virus-association.pdf", 
          eps_file = "../results/cough-data/coughs-virus-association.eps", 
          w = 10, h = 8)
```

### 2023-10-04 analysis/epi_analysis.Rmd
changes to plots

# number of cases by week
cases_by_week_pl <- epi_data %>%
  mutate(week = isoweek(date)) %>%
  filter(week != 6) %>%
  mutate(week = ifelse(week < 6, week - min(week) + 1, week - min(week))) %>%
  group_by(class, week) %>%
  summarize(cases = sum(new_cases),
            aircleaner = first(aircleaner)) %>%
  ungroup() %>%
  mutate(aircleaner = factor(aircleaner, levels = c("Yes", "No")),
         class = factor(class, levels = c("A", "B"))) %>%
  arrange(class, aircleaner) %>%
  ggplot(aes(x = factor(week), y = cases, fill = aircleaner, pattern = class)) +
  geom_bar_pattern(stat = "identity", color = "black", pattern_fill = "white", pattern_angle = 45,
                   pattern_density = 0.25, pattern_spacing = 0.05, width = .5) +
  labs(x = "Study week", y = "Number of cases", fill = "Air cleaner", pattern = "Class", title = "a") +
  scale_fill_manual(values = rev(wes_palette("Royal1")[1:2])) +
  scale_x_discrete(breaks = 1:7) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.05)), breaks = seq(0, 10, 2)) +
  scale_pattern_manual(values = c(A = "stripe", B = "none")) +
  theme_custom() +
  theme(legend.position = c(0.13, 0.8),
        legend.key.width = unit(0.5, "cm"),
        legend.key.height = unit(0.3, "cm"),
        plot.title.position = "plot") +
  guides(fill = guide_legend(nrow = 1, override.aes = list(pattern = "none", order = 2)),
         pattern = guide_legend(nrow = 1, override.aes = list(fill = "white"), order = 1))

save_plot(cases_by_week_pl,
          pdf_file = "../results/epi-data/cases_by_week.pdf",
          eps_file = "../results/epi-data/cases_by_week.eps",
          w = 16, h = 8) 
```

@@

```{r}
arr <- spread_draws(latInfMod, `beta[1]`) %>%
  rename(effect = `beta[1]`) %>%
  dplyr::select(effect) %>%
  mean_qi(.width = c(0.5, 0.8, .95)) %>%
  mutate(across(c(effect, .lower, .upper), exp))
arr
```

@@

save_plot(avoid_infections_pl, 
          pdf_file = "../results/epi-data/avoided-infections.pdf",
          eps_file = "../results/epi-data/avoided_infections.eps",
          w = 16, h = 8)
```

>>>>

# number of cases by week
cases_by_week_pl <- epi_data %>%
  group_by(class, aircleaner) %>%
  summarize(cases = sum(new_cases)) %>%
  ungroup() %>%
  mutate(aircleaner = factor(aircleaner, levels = c("No", "Yes")),
         class = factor(class, levels = c("A", "B"))) %>%
  arrange(class, aircleaner) %>%
  ggplot(aes(x = aircleaner, y = cases, fill = aircleaner)) +
  geom_bar_pattern(mapping = aes(pattern = class),
                   stat = "identity", color = "black", pattern_fill = "white", pattern_angle = 45,
                   pattern_density = 0.25, pattern_spacing = 0.05, width = .5) +
  geom_text(data = epi_data %>% group_by(aircleaner) %>% summarize(cases = sum(new_cases)) %>% ungroup(),
            mapping = aes(label = cases),
            size = 8 / cm(1), vjust = -1) +
  labs(x = "Air cleaner", y = "Number of cases", fill = "Air cleaner", pattern = "Class", title = "a") +
  scale_fill_manual(values = wes_palette("Royal1")[1:2]) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.1)), breaks = scales::pretty_breaks(4)) +
  scale_pattern_manual(values = c(A = "stripe", B = "none")) +
  theme_custom() +
  theme(legend.position = "top",
        legend.box = "horizontal",
        legend.direction = "horizontal",
        legend.key.width = unit(0.5, "cm"),
        legend.key.height = unit(0.3, "cm"),
        plot.title.position = "plot") +
  guides(fill = "none",
         pattern = guide_legend(nrow = 1, override.aes = list(fill = "white"), order = 1))

cases_by_week_pl

save_plot(cases_by_week_pl,
          pdf_file = "../results/epi-data/cases_by_condition.pdf",
          eps_file = "../results/epi-data/cases_by_condition.eps",
          w = 6, h = 8) 
```

@@

```{r}
arr <- spread_draws(latInfMod, `beta[1]`) %>%
  rename(effect = `beta[1]`)

sum(arr$effect<0) / nrow(arr) * 100

arr <- arr %>%
  dplyr::select(effect) %>%
  mean_qi(.width = c(0.5, 0.8, .95)) %>%
  mutate(across(c(effect, .lower, .upper), exp))
arr
```

@@

save_plot(avoid_infections_pl, 
          pdf_file = "../results/epi-data/avoided-infections.pdf",
          eps_file = "../results/epi-data/avoided_infections.eps",
          w = 10, h = 8)
```

### 2023-10-04 analysis/mol_analysis.Rmd
changes to plots

tnet_pl <- tnet %>%
  ggplot(aes(y = date_infection, x = virus, fill = virus, size = n)) +
  facet_wrap(~ class, ncol = 2, scales = "free_x") +
  geom_point(shape = 21, color = "black") +
  geom_segment(aes(y = from, yend = to, xend = virus), size = 1,
               arrow = arrow(length = unit(0.2, "cm")), color = "black") +
  labs(size = "Number of infections", fill = "Virus") +
  coord_y_datetime(ylim = c(max(tnet$date_infection), min(tnet$date_infection))) +
  scale_y_datetime(date_breaks = "1 week", date_labels = "%b %d") +
  scale_size_discrete(range = c(4,8)) +
  scale_fill_manual(values = wes_palette("IsleofDogs1")) +
  theme_custom() +
  theme(legend.position = "top",
        legend.direction = "horizontal",
        legend.box = "vertical",
        #plot.title.position = "plot",
        axis.title = element_blank(),
        #axis.text.x = element_blank(),
        #axis.ticks.x = element_blank(),
        panel.spacing = unit(1, "cm"),
        panel.grid.major.x = element_line(),
        panel.grid.minor.y = element_blank(),
        strip.text.x = element_text(size = 10, margin = margin(b = 10))) +
  guides(fill = "none",
         size = guide_legend(nrow = 1, order = 1))

>>>>

mirror_scales <- list(scale_x_discrete(limits = rev), scale_x_discrete())

tnet_pl <- tnet %>%
  ggplot(aes(y = date_infection, x = virus, fill = virus, size = n)) +
  facet_wrap(~ class, ncol = 2, scales = "free_x") +
  ggh4x::facetted_pos_scales(x = mirror_scales) +
  geom_point(shape = 21, color = "black") +
  geom_segment(aes(y = from, yend = to, xend = virus), size = 1,
               arrow = arrow(length = unit(0.2, "cm")), color = "black") +
  labs(size = "Number of infections", fill = "Virus") +
  coord_y_datetime(ylim = c(max(tnet$date_infection), min(tnet$date_infection))) +
  scale_y_datetime(date_breaks = "1 week", date_labels = "%b %d") +
  scale_size_discrete(range = c(4,8)) +
  scale_fill_manual(values = wes_palette("IsleofDogs1")) +
  theme_custom() +
  theme(legend.position = "bottom",
        legend.direction = "horizontal",
        legend.box = "vertical",
        #plot.title.position = "plot",
        axis.title = element_blank(),
        #axis.text.x = element_blank(),
        #axis.ticks.x = element_blank(),
        panel.spacing = unit(1, "cm"),
        panel.grid.major.x = element_line(),
        panel.grid.minor.y = element_blank(),
        strip.text.x = element_text(size = 10, margin = margin(b = 10))) +
  guides(fill = "none",
         size = guide_legend(nrow = 1, order = 1))

### 2023-10-04 analysis/study_comaprison.Rmd
changes to plots

```{r}
pos_samples <- data.frame(
  year = factor(c(rep(2022, 3), rep(2023, 3)), levels = c(2022, 2023)),
  type = factor(rep(c("Saliva", "Bioaerosols", "HEPA-filter"), times = 2), levels = c("Saliva", "Bioaerosols", "HEPA-filter")),
  n = c(c(21, 10, 8), c(50, 2, 4))
) %>%
  ggplot(aes(x = n, y = year, pattern = year, color = year, pattern_color = year)) +
  geom_bar_pattern(stat = "identity", fill = "white", pattern_density = 0.1, pattern_spacing = 0.1, width = .75) +
  geom_text(aes(label = n), size = 8 / cm(1), hjust = -1) +
  facet_wrap(~ type, ncol = 1) +
  scale_x_continuous(expand = expansion(add = c(0,9.5))) +
  scale_color_manual(values = wes_palette("Darjeeling2")[c(2, 5)]) +
  scale_pattern_color_manual(values = wes_palette("Darjeeling2")[c(2, 5)]) +
  labs(y = "Study year", x = "Frequency", title = "b") +
  theme_custom() +
  theme(legend.position = "none",
        plot.title.position = "plot")

@@

particle <- data.frame(
  year = factor(c(rep(2022, 15), rep(2023, 15)), levels = c(2022, 2023)),
  variable = factor(c(rep(c("Cn", "PM1", "PM25", "PM4", "PM10"), each = 3, times = 2)), levels = c("Cn", "PM1", "PM25", "PM4", "PM10")),
  interval = rep(c("Mean", "Lower", "Upper"), times = 5),
  estimate = c(c(39.24, 3.88, 68.80, 
                 41.05, 6.62, 67.98,
                 45.12, 19.66, 63.16,
                 46.49, 27.26, 61.72,
                 46.60, 29.99, 59.49),
               c(76.83, 63.20, 86.28,
                 76.79, 64.84, 85.46,
                 72.86, 64.24, 79.66,
                 70.77, 63.46, 76.97,
                 99.99, 99.94, 100.00))
) %>%
  dcast(year + variable ~ interval) %>%
  ggplot(aes(y = year, color = year)) +
  facet_wrap(~ variable, nrow = 1, dir = "h", labeller = as_labeller(vars_labels_no_units, label_parsed)) +
  geom_errorbar(mapping = aes(xmin = Lower, xmax = Upper), lineend = "square", size = 1, width = .05) +
  geom_point(mapping = aes(x = Mean), shape = 23, size = 2, fill = "white") +
  scale_color_manual(values = wes_palette("Darjeeling2")[c(2, 5)]) +
  scale_x_continuous(expand = expansion(mult = c(0, 0.1)), breaks = c(0, 50, 100), limits = c(0, 100)) +
  labs(y = "Study year", x = "Estimated reduction (%)", title = "c") + 
  theme_custom() +
  theme(legend.position = "none",
        plot.title.position = "plot",
        panel.spacing = unit(.5, "lines"))

@@

```{r}
rr <- data.frame(
  year = factor(c(rep(2022, 3), rep(2023, 3)), levels = c(2022, 2023)),
  interval = rep(c("Mean", "Lower", "Upper"), times = 2),
  estimate = c(c(1.00, 0.22, 2.067), c(0.72, 0.44, 1.15))
) %>%
  dcast(year ~ interval) %>%
  ggplot(aes(y = year, color = year)) +
  geom_vline(aes(xintercept = 1), linetype = "dashed") +
  geom_errorbar(mapping = aes(xmin = Lower, xmax = Upper), lineend = "square", size = 1, width = .05) +
  geom_point(mapping = aes(x = Mean), shape = 23, size = 2, fill = "white") +
  labs(y = "Study year", x = "Adjusted risk ratio (%)", title = "d") + 
  scale_color_manual(values = wes_palette("Darjeeling2")[c(2, 5)]) +
  theme_custom() +
  theme(legend.position = "none",
        plot.title.position = "plot")

>>>>

```{r}
pos_samples <- data.frame(
  year = factor(c(rep(2022, 3), rep(2023, 3)), levels = c(2022, 2023)),
  type = factor(rep(c("Saliva", "Bioaerosols", "HEPA-filter"), times = 2), levels = c("Saliva", "Bioaerosols", "HEPA-filter")),
  n = c(c(21, 10, 8), c(50, 2, 4))
) %>%
  ggplot(aes(x = n, y = year, pattern = year, color = year, pattern_color = year)) +
  geom_bar_pattern(stat = "identity", fill = "white", pattern_density = 0.1, pattern_spacing = 0.1, width = .75) +
  geom_text(aes(label = n), size = 8 / cm(1), hjust = -1) +
  facet_wrap(~ type, ncol = 1) +
  scale_x_continuous(expand = expansion(add = c(0,9.5))) +
  scale_color_manual(values = wes_palette("Darjeeling2")[c(2, 5)]) +
  scale_pattern_color_manual(values = wes_palette("Darjeeling2")[c(2, 5)]) +
  labs(y = "Study year", x = "Frequency of positive samples", title = "b") +
  theme_custom() +
  theme(legend.position = "none",
        plot.title.position = "plot")

@@

particle <- data.frame(
  year = factor(c(rep(2022, 15), rep(2023, 15)), levels = c(2022, 2023)),
  variable = factor(c(rep(c("Cn", "PM1", "PM25", "PM4", "PM10"), each = 3, times = 2)), levels = c("Cn", "PM1", "PM25", "PM4", "PM10")),
  interval = rep(c("Mean", "Lower", "Upper"), times = 5),
  estimate = c(c(39.24, 3.88, 68.80, 
                 41.05, 6.62, 67.98,
                 45.12, 19.66, 63.16,
                 46.49, 27.26, 61.72,
                 46.60, 29.99, 59.49),
               c(76.83, 63.20, 86.28,
                 76.79, 64.84, 85.46,
                 72.86, 64.24, 79.66,
                 70.77, 63.46, 76.97,
                 99.99, 99.94, 100.00))
) %>%
  dcast(year + variable ~ interval) %>%
  ggplot(aes(y = year, color = year)) +
  facet_wrap(~ variable, nrow = 1, dir = "h", labeller = as_labeller(vars_labels_no_units, label_parsed)) +
  geom_errorbar(mapping = aes(xmin = Lower, xmax = Upper), lineend = "square", size = 1, width = .05) +
  geom_point(mapping = aes(x = Mean), shape = 23, size = 2, fill = "white") +
  scale_color_manual(values = wes_palette("Darjeeling2")[c(2, 5)]) +
  scale_x_continuous(expand = expansion(mult = c(0, 0.1)), breaks = c(0, 50, 100), limits = c(0, 100)) +
  labs(y = "Study year", x = "Estimated reduction in particle concentration (%)", title = "c") + 
  theme_custom() +
  theme(legend.position = "none",
        plot.title.position = "plot",
        panel.spacing = unit(.5, "lines"))

@@

```{r}
rr <- data.frame(
  year = factor(c(rep(2022, 3), rep(2023, 3)), levels = c(2022, 2023)),
  interval = rep(c("Mean", "Lower", "Upper"), times = 2),
  estimate = c(c(1.00, 0.22, 2.067), c(0.72, 0.44, 1.15))
) %>%
  dcast(year ~ interval) %>%
  ggplot(aes(y = year, color = year)) +
  geom_vline(aes(xintercept = 1), linetype = "dashed") +
  geom_errorbar(mapping = aes(xmin = Lower, xmax = Upper), lineend = "square", size = 1, width = .05) +
  geom_point(mapping = aes(x = Mean), shape = 23, size = 2, fill = "white") +
  labs(y = "Study year", x = "ARR of infection with air cleaners (%)", title = "d") + 
  scale_color_manual(values = wes_palette("Darjeeling2")[c(2, 5)]) +
  theme_custom() +
  theme(legend.position = "none",
        plot.title.position = "plot")
